CommonMind Consortium: DLPFC

### 2020-09-20 combined_analysis/diff.networks.Rmd
Update diff networks

@@

df_module_enrich.Sex = enrich.test( df_module.Sex, go.gs, df_cohort2$Module[i], 150).  
```

@@

## DE enrichment
```{r cameraPR.Dx_Sex}
res_enrich_DE = enrich_module_DE( df_module_enrich.Dx_Sex )

>>>>

```{r load.WES}
df_schema = fread(synGet('syn22343823')$path)

df_schema2 = df_schema[,data.frame(ENSEMBL = Gene,
									OR1 = `OR (Class I)`,
									OR2 = `OR (Class II)`,
									P.value = `P meta`)]

@@

df_module_enrich.Sex = enrich.test( df_module.Sex, go.gs, df_cohort2$Module[i], 150) 
```

@@

## DE enrichment
```{r cameraPR.Dx_Sex}
res_enrich_DE = enrich_module_DE( df_module.Dx_Sex )
